---
title: "R-Worksheet4"
author: "Allissa Nguyen"
date: "11/3/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) 
library(MASS)
```

## Visualizing Data using ggplot Graphs
```{r load crabs data}
mycrabs = MASS::crabs
```


Create a graph comparing carapace width to carapace length using a geom_point() graph.  
```{r crabs graph}
mycrabs %>% 
  ggplot() +
  geom_point(mapping = aes(x = CW, y = CL)) +
  labs(title = "Carapace Width vs Carapace Length",
       x = "Carapace Width",
       y = "Carapace Length")
```


Now create a boxplot comparing BD (body depth) measurement for each species.  Use the geom_boxplot() tool.  Your graph should look like this.
```{r}
mycrabs %>% 
  ggplot() +
  geom_boxplot(mapping = aes(sp, BD)) +
  labs(title = "Species Comparison of Body Depth",
       x = "Species",
       y = "Body Depth")
```


Now create additional detail by color coding the observations by sex.  Use the the facet_wrap command, with the ~ element specifier.  Your graph should look like this.
```{r}
mycrabs %>% 
  ggplot() +
  geom_point(mapping = aes(x = CW, y = CL, color = sex)) +
  facet_wrap(~sp) +
  labs(title = "Carapace Width vs Carapace Length",
       x = "Carapace Width",
       y = "Carapace Length")
```


Continue your analysis by combining the species and sex data into a single combined "key" field called spsex.  Use the new field to create a series of side-by-side boxplots of body depth identified by sex and species.  Your graph should look like this.

Creating new key
```{r}
mycrabs["spsex"] <- paste(mycrabs$sp, mycrabs$sex, sep = "")
```


```{r}
mycrabs %>% 
  ggplot() +
  geom_boxplot(aes(spsex, BD))
```


Now make a histogram showing the body depth for all the sexes and species.  Use the geom_histogram() tool.  Your graph should look like this.
```{r}
mycrabs %>% 
  ggplot() +
  geom_histogram(aes(BD))+
  labs(title = "Distribution of Body Depth",
       x = "Body Depth",
       y = "Count")
```

